### 2013-10-02 chi2014/qualitative.tex
revision

We identified three categories of strategy. The first, \emph{feature exploration}, is specific to the MP3 player problem presented in the paper. This category entails focussing on specific features a device possesses and leveraging them as the basis for generating new ideas. The second category expands on the \emph{riffing} phenomenon introduced earlier, identifying six(?) different types of riffing exployed. Finally, \emph{time-saving} strategies are those that do not neccesarily impact the kinds of ideas generated, but allow the participant to generate at a faster rate.

@@

@@

We use personas to capture collections of strategy use we see repeated across participants. While some strategies proved discriminatory, others were used more or less equally by all personas. Drill-down riffing, pairing and language riffing, while interesting strategies, are either minimal in the makeup of a run or have no impact of the subjective quality of the resulting ideas.

Six personas were identified: quitters, lazy creatives, diligent struggles, lazy strugglers, hard workers, and over-deliverers. These personas are described below. A summary, in terms of strategies used, is in Table TAB.

@@

\emph{Lazy creatives} provide primarily uncommon responses, but do not put any particular effort into the responses. They employ the brevity, reach back and exhaustive mutation strategies to a great extent. These participants seem like prime targets for future interventions, as their ideas are of interest but they focus their strategies towards rapid completion. Lazy creatives employ minimal feature utilization.

@@

\begin{table*}
    \begin{tabular}{|l|l|l|}
        \hline
        \textbf{Persona} & \textbf{Common strategies} & \textbf{Uncommon strategies} \\
        \hline
        Quitters & cop-outs, exhaustive mutation & \\
        Lazy creatives & & \\
        Diligent strugglers & & \\
        Lazy struggles & & \\
        Hard workers & & \\
        Over-deliverers & & \\
        \hline
    \end{tabular}
\end{table*}

>>>>

We identified four categories of strategy. The first, \emph{feature exploration}, is specific to the MP3 player problem presented in the paper. This category entails focussing on specific features a device possesses and leveraging them as the basis for generating new ideas. The second category expands on the \emph{riffing} phenomenon introduced earlier, identifying six(?) different types of riffing exployed. \emph{Time-saving} strategies are those that allow the participant to generate at a faster rate. Finally, the \emph{humour} strategy emphasizes generating ideas that are amusing rather than practical.

@@

Time-saving strategies tend to negatively impact the quality of responses. While there are succinct, creative responses, many brief responses are often a sign that the ideas within the run are "low-hanging fruit". Cop-out ideas are poor quality by definition.

\subsubsection{Humour}

Some participants used \emph{humour} as a method of generating ideas. For example, one response given was "glue it to the side walk and let the fun ensue". While ideas generated under this strategy are impractical individually, this strategy is most often employed by participants who otherwise take the idea generation task seriously and perform successfully.

@@

We use personas to capture collections of strategy use we see repeated across participants. 
Six personas were identified: quitters, lazy creatives, diligent struggles, lazy strugglers, hard workers, and over-deliverers. These personas are described below. A summary, in terms of strategies used, is in Table TAB.

@@

\emph{Lazy creatives} provide primarily uncommon responses, but do not put effort into the responses. They employ brevity, reach back and exhaustive mutation strategies to a great extent. These participants seem like prime targets for future interventions, as their ideas are of interest but they focus their strategies towards rapid completion. Lazy creatives employ minimal feature utilization.

@@

\begin{table*}
    \begin{tabular}{|l|p{0.35\linewidth}|l|}
        \hline
        \textbf{Persona} & \textbf{Common strategies} & \textbf{Rare strategies} \\
        \hline
        Quitters & cop-outs, exhaustive mutation & follow-up riffing \\
        \hline
        Lazy creatives & exploratory riffing, specificity riffing, \newline
        exhaustive mutation, brevity, reach-backs  & follow-up riffing  \\
        \hline
        Diligent strugglers & exploratory riffing & exhaustive mutation, brevity, \newline
        follow-up riffing \\
        \hline
        Lazy strugglers & exhaustive mutation, exploratory riffing, \newline
        cop-outs, brevity  & follow-up riffing \\
        \hline
        Hard workers & feature use, humour, \newline
        exploratory riffing, specificity riffing  & follow-up riffing, exhaustive mutation \\
        \hline
        Over-deliverers & feature use & riffing, reach-backs, brevity \\
        \hline
    \end{tabular}
    \caption{Strategies used by personas}
\end{table*}
